Democracy, Public Support, and Measurement Uncertainty

### 2021-07-20 paper/dcpo_demsupport.Rmd
adjust citation.

Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent variable, the dependent variable, and control variables to account for the uncertainty from the measurement model as well as dependent and control variables.
To do this, we take 900 draws from the distribution of public democratic support and corruption index, duplicate each article's analysis dataset of variables without “measurement error” 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987 and employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015].
@Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
We also employ one alternative technique known as “method of composition” (MOC)  [@treier_democracy_2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].

@@

To ensure the robustness of our analysis, we apply another method to account for uncertainty.
The method we employ is "method of composition" (MOC).
It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@treier_democracy_2008].
To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
In multiple overimputation (MO, the method used in the main article), the explanatory variable with measurement errors is regarded as missing data $x^{mis}$ with an observed proxy $w$ under the assumption of "Missing at Random" and "Ignorable Measurement Mechanism Assignment" [@Blackwell2017].
The explanatory variables without error are denoted $x^{obs}$.
*Personally, I think we should be careful to use MO since our approach is not MO. I will go back here later.* 
The parameter likelihood is then

>>>>

Following this line, after replicating the original analyses with point estimates, we take the distribution of the latent variable, the dependent variable, and control variables to account for the uncertainty from the measurement model as well as dependent and control variables.
To do this, we take 900 draws from the distribution of public democratic support and corruption index, duplicate each article's analysis dataset of variables without “measurement error” 900 times, and assign them to each a different random draw from the posterior distribution of democracy indices.
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987 and employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015].
@Blackwell2017a's multiple overimputation (MO) uses the same logic to correct sampling variance.
We also employ one alternative technique known as “method of composition” (MOC)  [@Treier2008, p. 215] as a robustness check [see the Online Supplementary Material \@ref(moc)].

@@

To ensure the robustness of our analysis, we apply another method to account for uncertainty.
The method we employ is "method of composition" (MOC).
It is a common method for Monte Carlo integration, but can also be applied for addressing uncertainty [@Treier2008].
To compare these two methods, let's denote `y` as a vector of the outcome variable [either institutional democracy in @Claassen2020a or the changes in mass support of democracy in @Claassen2020b]. 
Let $x$ (variables without subscript are used to denote vectors of observations, viz., $x$ = ($x_1$,......, $x_i$)) be a vector of the explanatory variable (e.g., mass support or institutional democracy) and $\theta$ be the parameter of interest.
In multiple overimputation (MO, the method used in the main article), the explanatory variable with measurement errors is regarded as missing data $x^{mis}$ with an observed proxy $w$ under the assumption of "Missing at Random" and "Ignorable Measurement Mechanism Assignment" [@Blackwell2017].
The explanatory variables without error are denoted $x^{obs}$.
*Personally, I think we should be careful to use MO since our approach is not MO. I will go back here later.* 
The parameter likelihood is then
